% Copyright (C) 2017 - Juan Pablo Carbajal
%
% This work is licensed under a
% Creative Commons Attribution-ShareAlike 4.0 International License.
%
% You should have received a copy of the license along with this
% work. If not, see <http://creativecommons.org/licenses/by-sa/4.0/>.

\documentclass[10pt,english,final,a4paper]{exam}

\include{preamble}

\pagestyle{headandfoot}
\runningheadrule
\firstpageheader{}{}{}
\runningheader{1D Regression Exercises}{}{January 2018}
\firstpagefooter{}{\doclicenseThis}{}
\runningfooter{}{}{\doclicenseImage}
\runningfootrule

%\author{Juan Pablo Carbajal}
%\date{January 2018}
%\title{Msc. thesis S. Rusca: regression}

%\qformat{Exercise~\thequestion: \thequestiontitle \hfill}

\begin{document}

\begin{center}
{\Large 1D Regression}\\
Juan Pablo Carbajal\\
January 2018
\end{center}

\vspace{1.5em}

%Linear least-squares, Polynomial, Splines, Nonlinear least-squares, GP

\section{Definitions}
A \textbf{dataset} is a set of input-output data pairs 
\begin{equation}
\lbrace \left(\bm{x}_i, y_i\right), \quad i = 1, \ldots, N\rbrace
\end{equation}
\noindent where $N$ is the size of the dataset, $\bm{x}_i \in \mathbb{R}^n$ is the $i$-th sample (or observation) of the input vector, and $y_i \in \mathbb{R}$
is the $i$-th sample of the output.

\section{Training, validation and testing}
\begin{questions}
\titledquestion{Splitting the dataset}
Write a function that splits a dataset into two random complementary proper subsets.
\titledquestion{Shuffling the dataset}
Write a function that exchanges elements from two complementary sets.
\end{questions}

\section{Cross-validation}
\begin{questions}
\question Given an dataset of size $N$, write a function that produces all subsets of size $N-1$.
\titledquestion{Leave-one-out cross-validation}
The file \texttt{interpolation1D\_poly1.dat} contains two noiseless datasets with the same inputs.
\begin{parts}
\part Find the simplest polynomial model that interpolates the data using leave-one-out cross-validation. \hint{\texttt{polyfit}}

\part Compute the uncertainty in the polynomial model using second output of the function \texttt{polyfit}

\part Compute the uncertainty in the model using the jackknife method

\part Compute the uncertainty in the intrapolation by propagating model uncertainties to the output.

\part Compute the uncertainty in the intrapolation using the leave-one-out out-of-sample error estimation.

\end{parts}

\question Redo all parts of the previous question using a \emph{linear filter}:

\begin{equation}
y (\bm{x}) = \sum_{i=1}^N y_i \varphi(\bm{x}, \bm{x}_i)
\end{equation}

In addition answer the following:

\begin{parts}
\part Is this a linear model?

\part Use the functions

\begin{align}
\varphi_{L}(x,x_i) &=  \alpha(x) \frac{x   - x_i}{\sigma} + 1, \quad \alpha(x) = \begin{cases}
0  & x < x_i - \sigma \text{ or } x > x_i + \sigma\\
1  & x_i - \sigma \leq x \leq x_i\\
-1 & x_i \leq x \leq x_i + \sigma
\end{cases}\\
\varphi_{SE}(x,x_i) &= \exp \left( -\frac{(x - x')^2}{2 \sigma^2} \right)
\end{align}

\noindent to perform the interpolation and find the best value for the parameter $\sigma$ using cross-validation.

\end{parts}

\end{questions}

\section{Linear mixtures}
\begin{questions}
\question The 10 signals in \texttt{interpolation\_mixture.dat} are believed to be mixtures of the
following responses:
\begin{align}
y_{A}(t) &= \frac{1}{\sqrt{\kappa t}}, \quad t > 0\\
y_{B}(t) &= \sin \left( 2 \pi f \left(t - t_0\right) \right)\\
y_{C}(t) &= t^2 \exp \left( - \eta (t-\xi)^2\right)\\
y_{D}(t) &= \frac{1}{2} \left( 1 - \tanh (\nu (t - \delta)) \right)\\
\end{align}
\noindent where all parameters are positive real numbers.
\begin{parts}
\part Write a function to interpolate data using these responses
\part Find the value of the parameters that interpolate the signals in the file
\part What responses were present in which signal?
\end{parts}
\end{questions}

%\section{Input and output transformations}
%Explore the datasets in the files \texttt{interpolation1D\_warp*.dat}.
%\begin{questions}
%\question What is the simplest polynomial model that can interpolate these datasets?
%\question Find a model (not a polynomial) for each dataset that can interpolate the data and compute the uncertainty in the predictions of the model.
%\end{questions}

%\section{Special functions and Hilbert spaces}
%\begin{questions}
%\titledquestion{Fourier}
%\begin{parts}
%\part Shanon-Nyquist
%\end{parts}
%\titledquestion{Legendre}
%\titledquestion{Chebishev}
%\end{questions}

%\section{Gaussian processes}
%\begin{questions}
%\titledquestion{Choosing covariance functions}
%\titledquestion{MAP vs. Posterior}
%\end{questions}

\end{document}
